Sampling Strategies in Decisions from Experience

### 2022-05-24 manuscript_appendix.Rmd
Review introduction
add appendix

```{r A-setup, include=FALSE}
knitr::opts_chunk$set(echo = F, #omit messages
                      fig.align = "l", #align figures to left margin
                      fig.pos = "t")
```

\begin{figure}
\caption{Effect of Switching Probability on Rates of False Risky and False Safe Choices for 2-Outcome Prospects with High Rank Outcomes of Different Probability}\label{fig:A-choice-rates}
\includegraphics{manuscript_files/figure-latex/A-choice-rates-1}
\textit{Note.} A note.
\end{figure}

@@

\begin{figure}
\caption{Parameter Estimates of the Weighting Function of Goldstein and Einhorn (1987) for Different Simulation Parameters}\label{fig:A-weighting-parameters}
\includegraphics{manuscript_files/figure-latex/A-weighting-parameters-1}
\end{figure}

@@

\begin{figure}
\caption{Parameter Estimates of the Value Function of Tversky and Kahneman (1992) and of the Logit Choice Rule for Different Simulation Parameters}\label{fig:A-value-parameters}
\includegraphics{manuscript_files/figure-latex/A-value-parameters-1}
\end{figure}

@@

\begin{figure}
\caption{Estimated Graphical Shapes of the Weighting and Value Function for Different Simulation Parameters}\label{fig:A-cpt-graphs}
\includegraphics{manuscript_files/figure-latex/A-cpt-graphs-1}
\end{figure}

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(echo = F, #omit messages
                      fig.align = "l" #align figures to left margin
                      )
```

Note that the figures presented in the appendix differ from those presented in the main text to the extent that the thresholds $\theta$ have a different meaning. 
That is, for the round-wise integration model, $\theta$ is not the absolute number of mean comparisons a prospect must win (absolute threshold), but the required difference in the number of wins between prospects (relative threshold).
For the summary integration model, $\theta$ is not the absolute cumulative sum across all sampled outcomes a prospect must reach (absolute threshold), but the differences in these sums between prospects.

@@

\begin{figure}
\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
\includegraphics{manuscript_files/figure-latex/choice-rates-roundwise-relative-1} \label{fig:choice-rates-roundwise-relative}
\end{figure}

@@

\begin{figure}
\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
\includegraphics{manuscript_files/figure-latex/choice-rates-summary-relative-1} \label{fig:choice-rates-summary-relative}
\end{figure}

@@

\begin{figure}
\caption{Parameter Estimates of the Weighting Function}
\includegraphics{manuscript_files/figure-latex/weighting-parameters-relative-1} \label{fig:weighting-parameters-relative}
\end{figure}

\begin{figure}
\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-relative-1} \label{fig:sensitivity-parameters-relative}
\end{figure}

\begin{figure}
\caption{Estimated Graphical Shape of CPT's Weighting and Value Function}
\includegraphics{manuscript_files/figure-latex/function-forms-relative-1} \label{fig:function-forms-relative}
\end{figure}
